A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2024-12-15 manuscript/manuscript.qmd
modified url repo

[**Analytic code sharing statement:**]{.underline} Code to reproduce this manuscript, including all figures and tables, can be found at <https://gitlab-scm.partners.org/drugepi/encore/encore-process-paper>.

>>>>

[**Analytic code sharing statement:**]{.underline} Code to reproduce this manuscript, including all figures and tables, can be found at <https://github.com/janickweberpals/encore-process-manuscript>.
